---
title: "Yelp Data Analysis"
author: "Snehal Damare"
date: "May 5, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

library(tidyverse) #  data manipulation and graphs
library(stringr) #  string manipulation
library(lubridate) #  date manipulation
library('wordcloud') #  wordcloud
library(tidytext) # tidy implementation of NLP methods
library(DT)       # table format display of data
library(leaflet) # maps

library(igraph) #  graphs
library(ggraph) #  graphs

library(topicmodels) # for LDA topic modelling 
library(tm) # general text mining functions, making document term matrixes
library(SnowballC) # for stemming

library(textcat)

library("rjson")
```

## R Markdown

We load the data from CSV files first. There are mainly two entities: Business and Reviews.

```{r}
reviews <- read_csv('C:/Users/Snehal/Fall18/Rutgers sprin 18 sem2/wrangling/project/yelp_review.csv')
business <- read_csv("D://Spring19//Data Wrangling//project//yelp_business.csv")
```

## Businee Analysis

```{r echo=FALSE}
fillColor = "lightblue"
fillColor2 = "goldenrod2"

```
```{r,message=FALSE,warning=FALSE}

datatable(head(business), style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))
```
EDA


```{r}

mean(business$review_count)
```
```{r}
ggplot(reviews, aes(x=stars))+
  geom_bar(stat="bin", bins= 9, fill="blue2") + 
  geom_text(stat='count', aes(label=..count..), vjust=1.6, color="white") +
  ggtitle("Star Counts") +
  xlab("Stars") + ylab("Count") +
  theme_minimal()
```
```{r}
install.packages("gridExtra")
library("gridExtra")

p1 <- business %>% ggplot(aes(x=as.factor(stars))) + geom_bar()
p2 <- business %>% ggplot(aes(x=review_count)) + geom_histogram(bins=50) + scale_x_log10()
layout <- matrix
grid.arrange(p1, p2)
#ggplot2::multiplot(p1, p2, layout=layout)
```


#Most Popular Categories

The most popular categories of business are plotted in the bar plot

```{r,message=FALSE,warning=FALSE}

categories = str_split(business$categories,";")
categories = as.data.frame(unlist(categories))
colnames(categories) = c("Name")

categories %>%
  group_by(Name) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(Name = reorder(Name,Count)) %>%
  head(10) %>%
  
  
  ggplot(aes(x = Name,y = Count)) +
  geom_bar(stat='identity',colour="white", fill =fillColor2) +
  geom_text(aes(x = Name, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Name of Category', y = 'Count', 
       title = 'Top 10 Categories of Business') +
  coord_flip() + 
  theme_bw()

```

#Top Ten Cities with the most Business parties mentioned in Yelp


We show the Top Ten Cities which has the most Business parties mentioned in Yelp

```{r,message=FALSE,warning=FALSE}

business %>%
  group_by(city) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(City = reorder(city,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = City,y = Count)) +
  geom_bar(stat='identity',colour="white", fill ="skyblue") +
  geom_text(aes(x = City, y = 1, label = paste0("(",round(Count/1e3)," K )",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'City', y = 'Count of Reviews', 
       title = 'Top Ten Cities with the most Business parties in Yelp') +
  coord_flip() + 
  theme_bw()


```

#Map of the Businesses in Las vegas


Higher the review count larger is the size of marker on the map for the business.

```{r,message=FALSE,warning=FALSE}

LasvegasCoords = business %>% filter(city == "Las Vegas")

center_lon = median(LasvegasCoords$longitude,na.rm = TRUE)
center_lat = median(LasvegasCoords$latitude,na.rm = TRUE)

leaflet(LasvegasCoords) %>% addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircles(lng = ~longitude, lat = ~latitude,radius = ~sqrt(review_count))  %>%
  
  # controls
  setView(lng=center_lon, lat=center_lat,zoom = 13)

```



#Business with most Five Star Reviews from Users

The plot shows restuarants with most 5-star reviews.    



```{r,message=FALSE,warning=FALSE}

most5StarsReviews = reviews %>%
  filter(stars == 5) %>%
  group_by(business_id) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(BusinessID = reorder(business_id,Count)) %>%
  head(10)

most5StarsReviews = inner_join(most5StarsReviews,business)

most5StarsReviews %>%
  mutate(name = reorder(name,Count)) %>%
  ggplot(aes(x = name,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = "goldenrod2") +
  geom_text(aes(x = name, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Name of the Business', 
       y = 'Count', 
       title = 'Name of the Business and Count') +
  coord_flip() +
  theme_bw()

```


#EDA for Earl of sandwich restaurant

The location and category of the most liked business Earl of sandwich is shown below            


```{r,message=FALSE,warning=FALSE}

earl_of_sandwich = business %>% filter(business_id == "DkYS3arLOhA8si5uUEmHOw") %>%
  select(name,neighborhood,city,state,postal_code,categories)

datatable(head(earl_of_sandwich), style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

```

##Useful,funny,cool reviews

The following plot describes the number of **Useful, Funny and Cool** reviews.Most of the reviews are NOT useful , funny or cool.      


```{r,message=FALSE,warning=FALSE}

earl_of_sandwich_reviews = reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw")

earl_of_sandwich_reviews %>%
  group_by(useful) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(useful = reorder(useful,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = useful,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = useful, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Useful Reviews', 
       y = 'Count', 
       title = 'Useful Reviews and Count') +
  coord_flip() +
   theme_bw()


earl_of_sandwich_reviews %>%
  group_by(funny) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(funny = reorder(funny,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = funny,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor2) +
  geom_text(aes(x = funny, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Funny Reviews', 
       y = 'Count', 
       title = 'Funny Reviews and Count') +
  coord_flip() +
   theme_bw()


earl_of_sandwich_reviews %>%
  group_by(cool) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(cool = reorder(cool,Count)) %>%
  head(10) %>%
  
  ggplot(aes(x = cool,y = Count)) +
  geom_bar(stat='identity',colour="white", fill = fillColor) +
  geom_text(aes(x = cool, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Cool Reviews', 
       y = 'Count', 
       title = 'Cool Reviews and Count') +
  coord_flip() +
   theme_bw()


```

## Word Cloud of Earl of sandwich

A word cloud is a graphical representation of frequently used words in the text. The height of each word in this picture is an indication of frequency of occurrence of the word in the entire text. The words `steak, service, vegas,french,patio,bellagio,delicious, nice` are the words which have been used very frequently in the **reviews**.Note that if we choose a word which is not food related , it is **Service** and we will see in the subsequent sections of `sentiment analysis` and `topic modelling` , why this `keyword` is important.       



```{r,message=FALSE,warning=FALSE}

createWordCloud = function(train)
{
  train %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  count(word,sort = TRUE) %>%
  ungroup()  %>%
  head(40) %>%
  
  with(wordcloud(word, n, max.words = 40,colors=brewer.pal(8, "Dark2")))
}

createWordCloud(reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw"))

```

##Top Ten most common Words of the business Earl of sandwich

We examine the Top Ten Most Common words and show them in a bar graph. The words `sandwich, vegas, earbread, chicken,time, line, delicious` are the words which have been used very frequently in the **reviews**.         


```{r,message=FALSE,warning=FALSE}

earl_of_sandwich_reviews %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  filter(!word %in% c('food','restaurant')) %>%
  count(word,sort = TRUE) %>%
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  head(10) %>%
  
  ggplot(aes(x = word,y = n)) +
  geom_bar(stat='identity',colour="white", fill =fillColor) +
  geom_text(aes(x = word, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Word', y = 'Word Count', 
       title = 'Word Count') +
  coord_flip() + 
  theme_bw()

```

```{r}

 
    
    

```


## Sentiment Analysis - Postive and Not So Postive Words of **"Earl of sandwich"**

We display the Positive and Not So Positive words used by reviewers for the business `Earl of Sandwich`.We have used the **AFINN sentiment lexicon**, which provides numeric positivity scores for each word, and visualize it with a bar plot.

`Breathtaking,funnier,fun,fantastic,fabulous,ecstatic,brilliant,awesome,amazing` are some of the postive words that we have seen in the reviews of the business.        



```{r,message=FALSE,warning=FALSE}

positiveWordsBarGraph <- function(SC) {
  contributions <- SC %>%
    unnest_tokens(word, text) %>%
    count(word,sort = TRUE) %>%
    ungroup() %>%
    
    inner_join(get_sentiments("afinn"), by = "word") %>%
    group_by(word) %>%
    summarize(occurences = n(),
              contribution = sum(score))
  
  contributions %>%
    top_n(20, abs(contribution)) %>%
    mutate(word = reorder(word, contribution)) %>%
    head(20) %>%
    ggplot(aes(word, contribution, fill = contribution > 0)) +
    geom_col(show.legend = FALSE) +
    coord_flip() + theme_bw()
}

positiveWordsBarGraph(reviews %>%
                        filter(business_id == "DkYS3arLOhA8si5uUEmHOw"))


```





## Most Common Bigrams of **"Earl of Sandwich"**

A Bigram is a collection of Two words. We examine the most common Bigrams and plot them in a bar plot.

```{r,message=FALSE,warning=FALSE}

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}


visualize_bigrams <- function(bigrams) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
  
}

visualize_bigrams_individual <- function(bigrams) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a,end_cap = circle(.07, 'inches')) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}


reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw") %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  select(bigram,review_id) %>%
  head(10)


reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw") %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word) %>%
  filter(!word1 %in% c("earl","sandwich")) %>%
  unite(bigramWord, word1, word2, sep = " ") %>%
  group_by(bigramWord) %>%
  tally() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(bigramWord = reorder(bigramWord,n)) %>%
  head(10) %>%
  
  ggplot(aes(x = bigramWord,y = n)) +
  geom_bar(stat='identity',colour="white", fill = fillColor2) +
  geom_text(aes(x = bigramWord, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Bigram', 
       y = 'Count', 
       title = 'Bigram and Count') +
  coord_flip() + 
  theme_bw()

```


##Relationship among words

We explore the different relationship among the various words in `Mon Ami Gabi` reviews here through a network graph          


```{r,message=FALSE,warning=FALSE}

bigramsEOS <- reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw") %>%
  count_bigrams()

bigramsEOS %>%
  filter(n > 50) %>%
  visualize_bigrams()

```

###Relationship of words with **sandwich**

The following network diagram shows the words associated with the word **sandwich**       

```{r,message = FALSE,warning = FALSE}

bigramsEOS %>%
  filter(word1 == "sandwich" | word2 == "sandwich") %>%
  filter(n > 30) %>%
  visualize_bigrams()

```

###Relationship of words with **french**

The following network diagram shows the words associated with the word **french**       

```{r,message = FALSE,warning = FALSE}

bigramsEOS %>%
  filter(word1 == "italian" | word2 == "italian" ) %>%
  filter(n > 30) %>%
  visualize_bigrams()

```

# **Bacchanal Buffet**

The location and category of the most liked business **Bacchanal Buffet** is shown below            


```{r,message=FALSE,warning=FALSE}

bacchanal = business %>% filter(business_id == "RESDUcs7fIiihp38-d6_6g") %>%
  select(name,neighborhood,city,state,postal_code,categories)

datatable(head(bacchanal), style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

```

## Word Cloud of **Bacchanal Buffet**

```{r,message=FALSE,warning=FALSE}

bacchanal = reviews %>% filter(business_id == "RESDUcs7fIiihp38-d6_6g")

createWordCloud(bacchanal)

```


##Top Ten most common Words of the business **"Bacchanal Buffet"**

We examine the Top Ten Most Common words and show them in a bar graph.                     

```{r,message=FALSE,warning=FALSE}

bacchanal %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  filter(!word %in% c('food','restaurant')) %>%
  count(word,sort = TRUE) %>%
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  head(10) %>%
  
  ggplot(aes(x = word,y = n)) +
  geom_bar(stat='identity',colour="white", fill =fillColor) +
  geom_text(aes(x = word, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Word', y = 'Word Count', 
       title = 'Word Count') +
  coord_flip() + 
  theme_bw()

```

## Sentiment Analysis - Postive and Not So Postive Words of **Bacchanal Buffet**

We display the Positive and Not So Positive words used by reviewers for the business `Bacchanal Buffet`.We have used the **AFINN sentiment lexicon**, which provides numeric positivity scores for each word, and visualize it with a bar plot.
     


```{r,message=FALSE,warning=FALSE}

positiveWordsBarGraph(bacchanal)


```



##Relationship among words in Bacchanal Buffet

We explore the different relationship among the various words in `Bacchanal Buffet` here through a network graph          


```{r,message=FALSE,warning=FALSE}

bigrams_bacchanal <- bacchanal %>%
  count_bigrams()

bigrams_bacchanal %>%
  filter(n > 100) %>%
  visualize_bigrams()

```

###Relationship of words with **crab**

The following network diagram shows the words associated with the word **crab**       

```{r,message = FALSE,warning = FALSE}

bigramsMonAmiGabi %>%
  filter(word1 == "crab" | word2 == "crab" ) %>%
  visualize_bigrams()

```

###Relationship of words with **food**

The following network diagram shows the words associated with the word **food**       

```{r,message = FALSE,warning = FALSE}

bigramsMonAmiGabi %>%
  filter(word1 == "food" | word2 == "food" ) %>%
  filter(n > 10) %>%
  visualize_bigrams()

```


#Top Ten Business in Toronto

We list the Top Ten business in Toronto giving importance to the number of reviews and then to the number of stars obtained by the business.         


```{r,message=FALSE,warning=FALSE}

toronto_biz = business %>%
  filter(city == "Toronto") %>%
  arrange(desc(review_count,stars)) %>%
  select(name,neighborhood,address,review_count,stars) %>%
  head(10)

datatable(toronto_biz, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


```



# **Pai Northern Thai Kitchen**

##Word Cloud of business **Pai Northern Thai Kitchen**

```{r}

#r_BrIgzYcwo1NAuG9dLbpg

createWordCloud(reviews %>%
  filter(business_id == "r_BrIgzYcwo1NAuG9dLbpg"))

```


##Ten most common words used in reviews of business **Pai Northern Thai Kitchen**

We examine the Top Ten Most Common words and show them in a bar graph.                     

```{r,message=FALSE,warning=FALSE}

reviews %>%
  filter(business_id == "r_BrIgzYcwo1NAuG9dLbpg") %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  filter(!word %in% c('food','restaurant')) %>%
  count(word,sort = TRUE) %>%
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  head(10) %>%
  
  ggplot(aes(x = word,y = n)) +
  geom_bar(stat='identity',colour="white", fill =fillColor) +
  geom_text(aes(x = word, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Word', y = 'Word Count', 
       title = 'Word Count') +
  coord_flip() + 
  theme_bw()

```


## Sentiment Analysis - Postive and Not So Postive Words of **Pai Northern Thai Kitchen**

We display the Positive and Not So Positive words used by reviewers for the business `Pai Northern Thai Kitchen`.We have used the **AFINN sentiment lexicon**, which provides numeric positivity scores for each word, and visualize it with a bar plot.
     


```{r,message=FALSE,warning=FALSE}

positiveWordsBarGraph(reviews %>%
                        filter(business_id == "r_BrIgzYcwo1NAuG9dLbpg"))


```




##Relationship among words in **Pai Northern Thai Kitchen**

We explore the different relationship among the various words in `Pai Northern Thai Kitchen` here through a network graph          


```{r,message=FALSE,warning=FALSE}

bigrams_thai <- reviews %>%
  filter(business_id == "r_BrIgzYcwo1NAuG9dLbpg") %>%
  count_bigrams()

bigrams_thai %>%
  filter(n > 50) %>%
  visualize_bigrams()

```

###Relationship of words with **thai**

The following network diagram shows the words associated with the word **thai**       

```{r,message = FALSE,warning = FALSE}

bigrams_thai %>%
  filter(word1 == "thai" | word2 == "thai" ) %>%
  filter(n > 5) %>%
  visualize_bigrams()

```



#Topic Modelling   


Topic modeling is a method for **unsupervised classification of documents**, similar to clustering on numeric data, which finds natural groups of items even when we're not sure what we're looking for.

**Latent Dirichlet allocation (LDA)** is a particularly popular method for fitting a topic model. It treats each document as a mixture of topics, and each topic as a mixture of words. This allows documents to "overlap" each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language.

##LDA Function

Borrowing an awesome function from Rachael's Notebook

```{r}

# function to get & plot the most informative terms by a specificed number
# of topics, using LDA
top_terms_by_topic_LDA <- function(input_text, # should be a columm from a dataframe
                                   plot = T, # return a plot? TRUE by defult
                                   number_of_topics = 4) # number of topics (4 by default)
{    
    # create a corpus (type of object expected by tm) and document term matrix
    Corpus <- Corpus(VectorSource(input_text)) # make a corpus object
    DTM <- DocumentTermMatrix(Corpus) # get the count of words/document

    # remove any empty rows in our document term matrix (if there are any 
    # we'll get an error when we try to run our LDA)
    unique_indexes <- unique(DTM$i) # get the index of each unique value
    DTM <- DTM[unique_indexes,] # get a subset of only those indexes
    
    # preform LDA & get the words/topic in a tidy text format
    lda <- LDA(DTM, k = number_of_topics, control = list(seed = 1234))
    topics <- tidy(lda, matrix = "beta")

    # get the top ten terms for each topic
    top_terms <- topics  %>% # take the topics data frame and..
      group_by(topic) %>% # treat each topic as a different group
      top_n(10, beta) %>% # get the top 10 most informative words
      ungroup() %>% # ungroup
      arrange(topic, -beta) # arrange words in descending informativeness

    # if the user asks for a plot (TRUE by default)
    if(plot == T){
        # plot the top ten terms for each topic in order
        top_terms %>% # take the top terms
          mutate(term = reorder(term, beta)) %>% # sort terms by beta value 
          ggplot(aes(term, beta, fill = factor(topic))) + # plot beta by theme
          geom_col(show.legend = FALSE) + # as a bar plot
          facet_wrap(~ topic, scales = "free") + # which each topic in a seperate plot
          labs(x = NULL, y = "Beta") + # no x label, change y label 
          coord_flip() # turn bars sideways
    }else{ 
        # if the user does not request a plot
        # return a list of sorted terms instead
        return(top_terms)
    }
}


```

##Topic Modelling for Earl of Sandwich  

4 topics for the Earl of sandwich          

```{r,message=FALSE,warning=FALSE}

create_LDA_topics <- function(business_text,custom_stop_words)
{
  # create a document term matrix to clean
reviewsCorpus <- Corpus(VectorSource(business_text$text)) 
reviewsDTM <- DocumentTermMatrix(reviewsCorpus)

# convert the document term matrix to a tidytext corpus
reviewsDTM_tidy <- tidy(reviewsDTM)

# remove stopwords
reviewsDTM_tidy_cleaned <- reviewsDTM_tidy %>% # take our tidy dtm and...
    anti_join(stop_words, by = c("term" = "word")) %>% # remove English stopwords and...
    anti_join(custom_stop_words, by = c("term" = "word")) # remove my custom stopwords

top_terms_by_topic_LDA(reviewsDTM_tidy_cleaned$term, number_of_topics = 4)

}

eos = reviews %>%
  filter(business_id == "DkYS3arLOhA8si5uUEmHOw")

custom_stop_words <- tibble(word = c("earl","of","sandwich","restaurant","food","vegas"))

create_LDA_topics(eos,custom_stop_words)


```


##Topic Modelling for **Bacchanal Buffet**

4 topics for the **Bacchanal Buffet**          

```{r,message=FALSE,warning=FALSE}

custom_stop_words <- tibble(word = c("restaurant","food"))

create_LDA_topics(bacchanal,custom_stop_words)

```



#Phoenix City Analysis      

##Top Ten Business in Phoenix

We list the Top Ten business in Toronto giving importance to the number of reviews and then to the number of stars obtained by the business.         


```{r,message=FALSE,warning=FALSE}

city_biz = business %>%
  filter(city == "Phoenix") %>%
  arrange(desc(review_count,stars)) %>%
  select(name,neighborhood,address,review_count,stars) %>%
  head(10)

datatable(city_biz, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


```



## Topic Modelling for **Phoenix City**

We do a Topic Modelling on the reviews of a sample of **Ten Thousand Words** of Phoenix City.   

```{r,message=FALSE,warning=FALSE}

CityCoords = business %>%
  filter(city == "Phoenix")

city_words = inner_join(CityCoords,reviews) %>% select(date,text,review_id) %>% sample_n(10000)

custom_stop_words <- tibble(word = c("restaurant","food"))

create_LDA_topics(city_words,custom_stop_words)

```

We observe the themes of `Service  and time` being very dominant. The occurence of the word `chicken` among food items is present.             




## Word Cloud of **Phoenix City**

```{r,message=FALSE,warning=FALSE}

createWordCloud(city_words)

```


##Top Ten most common Words of the business **Phoenix City**

We examine the Top Ten Most Common words and show them in a bar graph.                     

```{r,message=FALSE,warning=FALSE}

city_words %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  filter(!word %in% c('food','restaurant')) %>%
  count(word,sort = TRUE) %>%
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  head(10) %>%
  
  ggplot(aes(x = word,y = n)) +
  geom_bar(stat='identity',colour="white", fill =fillColor) +
  geom_text(aes(x = word, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Word', y = 'Word Count', 
       title = 'Word Count') +
  coord_flip() + 
  theme_bw()

```





## Sentiment Analysis - Postive and Not So Postive Words of **Phoenix City**

We display the Positive and Not So Positive words used by reviewers for  `Phoenix City`.We have used the **AFINN sentiment lexicon**, which provides numeric positivity scores for each word, and visualize it with a bar plot.
     
```{r,message=FALSE,warning=FALSE}

positiveWordsBarGraph(city_words)


```


     
#**Bobby Q**

##Word Cloud of business **Bobby Q**

```{r,message=FALSE,warning=FALSE}

#VyVIneSU7XAWgMBllI6LnQ

bobby_q = reviews %>%
  filter(business_id == "VyVIneSU7XAWgMBllI6LnQ")

createWordCloud(bobby_q)


```


##Ten most common words used in reviews of business **Bobby Q**

We examine the Top Ten Most Common words and show them in a bar graph.                     

```{r,message=FALSE,warning=FALSE}

reviews %>%
  filter(business_id == "VyVIneSU7XAWgMBllI6LnQ") %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  filter(!word %in% c('food','restaurant')) %>%
  count(word,sort = TRUE) %>%
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  head(10) %>%
  
  ggplot(aes(x = word,y = n)) +
  geom_bar(stat='identity',colour="white", fill =fillColor) +
  geom_text(aes(x = word, y = 1, label = paste0("(",n,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Word', y = 'Word Count', 
       title = 'Word Count') +
  coord_flip() + 
  theme_bw()

```


## Sentiment Analysis - Postive and Not So Postive Words of **Bobby Q**

We display the Positive and Not So Positive words used by reviewers for the business `Bobby Q`.We have used the **AFINN sentiment lexicon**, which provides numeric positivity scores for each word, and visualize it with a bar plot.
     


```{r,message=FALSE,warning=FALSE}

positiveWordsBarGraph(reviews %>%
                        filter(business_id == "VyVIneSU7XAWgMBllI6LnQ"))


```




##Relationship among words in **Bobby Q**

We explore the different relationship among the various words in `Bobby Q` here through a network graph          


```{r,message=FALSE,warning=FALSE}

bigrams_restaurant <- reviews %>%
  filter(business_id == "VyVIneSU7XAWgMBllI6LnQ") %>%
  count_bigrams()

bigrams_restaurant %>%
  filter(n > 50) %>%
  visualize_bigrams()

```

```{r}
one_business <- reviews[which(reviews$business_id=='DkYS3arLOhA8si5uUEmHOw'),]
one_business_copy = one_business
attach(one_business_copy)
one_business <- one_business_copy[order(date),] 
detach(one_business_copy)

```

